\documentclass[letterpaper, 12pt]{article}

\usepackage[margin=1in]{geometry} % page Layout
\usepackage{enumitem} % enumeration labels
\usepackage[hidelinks]{hyperref} % url Links
\usepackage{fontawesome} % icons
\usepackage{xcolor} % colors
\usepackage{fontspec} % font specification
\usepackage{comment} % multiline comment
\usepackage{multicol} % multiple columns
\usepackage{sectsty}
\usepackage{ulem}
\usepackage{fancyhdr}
\usepackage{microtype}
%\usepackage{ragged2e}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\chead{}
\rhead{}
% \lfoot{\faGithub \space \href{https://www.github.com/patrickboateng}{patrickboateng}}
\lfoot{}
\cfoot{}
\rfoot{\footnotesize{page \ \vrule \ \thepage}}


% \newcommand{\fullwidthuline}[1]{%
% 	\par\noindent\uline{\hbox to \textwidth{#1\hfil}}\par
% }

% \sectionfont{\fullwidthuline}

\setlength{\parindent}{0pt}

\setmainfont{SourceSans3}

\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,
	urlcolor=blue,
}

%%%%% Custom Commands %%%%%%

\newcommand{\cvsection}[1]{

	\section*{#1} \vspace*{-0.8cm}%
	\rule{\linewidth}{1.5pt}\par
	%\rule[20pt]{\linewidth}{0.5pt} % underline
}

\newcommand{\verticalSpace}{4pt}

\begin{document}

%%% Header %%%

\begin{center}

	{\huge{\textbf{PATRICK BOATENG}}} \\ [\verticalSpace]

	P.O. Box 1694 \, \vrule \, Cantonment-Accra \\ [\verticalSpace]

	% Email
	\faEnvelope \space \href{mailto:boatengpatrick456@gmail.com}{\underline{boatengpatrick456@gmail.com}}
	\, \vrule \,
	% Phone
	\faPhone \space (+233) 248253743
	\, \vrule \,
	% Github
	\faGithub \space \href{https://www.github.com/patrickboateng}{\underline{patrickboateng}}

\end{center}

% EDUCATION"

\cvsection{EDUCATION}

\textbf{Bachelor's degree} \hfill \textbf{Sep 2017 - Nov 2021} \\ [\verticalSpace]
\textbf{Kwame Nkrumah University of Science and Technology}

\begin{itemize}[leftmargin=*]

	\item \textbf{Programme}: Bachelor of Science in Civil Engineering
	\item \textbf{Honor}: First Class [3.76/4.0] - \textit{WES iGPA Calculator}
	\item \textbf{Thesis}: Predicting the compressive strength of concrete using machine learning techniques.
	\item \textbf{Key Courses}: Introduction to Finite Element Methods \vrule \, Algebra \vrule \,
	      Numerical Analysis \vrule \, Statistics and Probability \vrule \, Differential Equation \vrule \,
	      lSoil and Rock mechanics \vrule \, Computer Aided Design (AutoCad) \vrule \, Computer Programming (MATLAB)
	      \vrule \, Construction Management

\end{itemize}

% RESEARCH INTEREST

\cvsection{RESEARCH INTEREST}

\begin{itemize}[leftmargin=*]

	\item \textbf{Machine learning for structural health monitoring}: Explore the application of machine
	      learning algorithms to monitor the health and predict the maintenance needs of civil structures
	      such as bridges, buildings, and dams using predictive models that use sensor data to detect
	      anomalies and structural weakness.

	\item \textbf{Finite Element Analysis of Structures:} I am passionate about applying advanced numerical
	      techniques to analyze and optimize structural designs. I focus on ensuring the safety and efficiency
	      of engineering structures, such as buildings and bridges.

	\item \textbf{Risk Analysis of Structures:} I want to specialize in evaluating and mitigating potential
	      risks associated with structural engineering projects. My research will aim at developing methodologies
	      for identifying vulnerabilities and enhancing the resilience of critical infrastructure.

	\item \textbf{Seismic Retrofitting:} Earthquake resilience is a critical concern in regions prone to seismic
	      activity. I want to develop retrofitting strategies to strengthen existing structures and minimize
	      damage during seismic events.

	\item \textbf{Machine Learning and Artificial Intelligence for Design Optimization:} I am exploring integrating
	      cutting-edge machine learning and artificial intelligence techniques into civil engineering. My research
	      will focus on using data-driven approaches to optimize the design and construction of structures, improving
	      efficiency and reducing resource consumption.

\end{itemize}

% WORK EXPERIENCE

\cvsection{WORK EXPERIENCE}

\textbf{Assistant Consulting Engineer} \hfill \textbf{Sep 2022 - Present} \\ [\verticalSpace]
\textbf{Heureka Consult Limited} \hfill \textbf{Full Time}

\begin{itemize}[leftmargin=*]

	\item Performed quality assurance and quality control procedures for construction projects, including
	      overseeing the Cardinal Namdini gold mine's water storage and tailings dams.
	\item Generated project and laboratory reports for the client.
	\item Conducted geotechnical site investigations for road projects, such as the Accra-Ofankor
	      road rehabilitation project.
	\item Analyzed laboratory test results and made engineering judgements.
	\item Conducted an assessment of structural soundness and stability of pre-existing structures.
	\item Developed a Microsoft Excel add-in capable of soil classification, accommodating both the
	      Unified Soil Classification System and the
	      American Association of State Highway and Transportation Officials classification systems.

\end{itemize}

\textbf{IT Consultant} \hfill \textbf{Sep 2021 - Aug 2022} \\ [\verticalSpace]
\textbf{Kwame Nkrumah University of Science and Technology} \hfill \textbf{National Service Personnel}

\begin{itemize}[leftmargin=*]

	\item Provided assistance in the digitization of manual tasks. For example,
	      I developed a simple database using Python and WxPython to keep track of
	      customers whose applications have been processed.
	\item Assisted and consulted in all IT related work.

\end{itemize}

\textbf{Site Engineer} \hfill \textbf{Apr 2020 - Nov 2020} \\ [\verticalSpace]
\textbf{Quatran Services Limited} \hfill \textbf{Intern}

\begin{itemize}[leftmargin=*]

	\item Conducted site supervision and implemented Quality Assurance and Quality Control
	      measures during the construction of the solvent extraction plant for Wilmar Africa.
	\item Ensured precise execution of structural drawings by interpreting and comprehending
	      the drawings accurately.
	\item Prepared weekly progress reports summarizing all the works completed on-site.

\end{itemize}

% HONORS AND AWARDS

\cvsection{HONORS AND AWARDS}

\begin{itemize}[leftmargin=*]

	\item \textbf{Provost Excellent Students Awards, College of Engineering (KNUST) in year 3 and 4}:
	      An award given to students who have demonstrated exceptional academic performance.

\end{itemize}

% RESEARCH EXPERIENCE

\cvsection{RESEARCH EXPERIENCE}

\textbf{Concrete compressive strength prediction} \hfill \faCalendar \space \textbf{Mar 2021 - Aug 2021}

\begin{itemize}[leftmargin=*]

	\item Employed various machine learning techniques to develop models for predicting the 28th day
	      compressive strength of concrete.
	      \href{https://www.github.com/patrickboateng/compressive-strength-prediction}{Repository Link}

\end{itemize}

% TECHNICAL SKILLS

\cvsection{TECHNICAL SKILLS}

\begin{itemize}[leftmargin=*]

	\item \textbf{Programming Languages}: Python \vrule \, C \vrule \, C++ \vrule \, Microsoft Excel VBA
	\item \textbf{Deep Learning Frameworks}: Pytorch
	\item \textbf{Machine Learning}: Scikit-learn \vrule \, XGBoost
	\item \textbf{Data Analysis}: Pandas \vrule \, Numpy
	\item \textbf{Software}: Microsoft Office Excel \vrule \, Latex \vrule \, AutoCad \vrule \, ETABS

\end{itemize}

% CERTIFICATIONS

\cvsection{CERTIFICATIONS}

\begin{itemize}[leftmargin=*]

	\item \textbf{Supervised Machine Learning: Regression and Classification}: A Coursera course offered
	      by DeepLearning.AI \& Standford University. Certificate earned at January 2023.
	      \href{https://www.coursera.org/account/accomplishments/certificate/VD8VT99H89J5}{Verification Link}

	\item \textbf{Advanced Learning Algorithms}: A  Coursera course offered by DeepLearning.AI \&
	      Standford University. Certificate earned at February 2023.
	      \href{https://www.coursera.org/account/accomplishments/certificate/7PRNGGJZ7YBR}{Verification Link}

	\item \textbf{Unsupervised Learning, Recommenders, Reinforcement Learning}: A Coursera course
	      offered by DeepLearning.AI \& Standford University. Certificate earned at March 2023.
	      \href{https://www.coursera.org/account/accomplishments/certificate/CTH6L4SBUL7S}{Verification Link}

	\item \textbf{Deep Neural Networks with PyTorch}: A Coursera course offered by IBM. Certificate
	      earned at June 2023.
	      \href{https://www.coursera.org/account/accomplishments/certificate/VW9E3WQXYPJ9}{Verification Link}

	\item \textbf{Introduction to Git and GitHub}: A Coursera course offered by Google. Certificate
	      earned at February 2021.
	      \href{https://www.coursera.org/account/accomplishments/certificate/3H3N24N688CQ}{Verification Link}

	\item \textbf{Python Crash Course}: A Coursera course offered by Google. Certificate earned at February 2021.
	      \href{https://www.coursera.org/account/accomplishments/certificate/ULTQVPQLDMZU}{Verification Link}

	\item \textbf{Operating Systems and You: Becoming a Power User}: A Coursera course offered by Google.
	      Certificate earned at February 2021.
	      \href{https://www.coursera.org/account/accomplishments/certificate/3N5CTQHU47X3}{Verification Link}

	\item \textbf{Excel Skills for Business: Essentials}: A Coursera course offered by Macquarie University.
	      Certificate earned at March 2021.
	      \href{https://www.coursera.org/account/accomplishments/certificate/7DPNK2A4CHMX}{Verification Link}

\end{itemize}

% PERSONAL PROJECTS

\cvsection{PERSONAL PROJECTS}

\begin{itemize}[leftmargin=*]

	\item \textbf{geolysis}: An open-source software for geotechnical engineering analysis and modelling. \par
	      \href{https://www.github.com/patrickboateng/geolysis}{Repository Link}

	\item \textbf{compressive-strength-prediction}: Concrete Compressive Strength Prediction Using Machine
	      Learning and Deep Learning Techniques.
	      \href{https://github.com/patrickboateng/compressive-strength-prediction}{Repository Link}

	\item \textbf{makepackage}: A Python package for packaging python code. (\textit{Contributor/Collaborator}) \par
	      \href{https://github.com/nyggus/makepackage/graphs/contributors}{Repository Link}

\end{itemize}

% REFERENCES

\cvsection{REFERENCES}

\textbf{[\href{mailto:boatengpatrick456@gmail.com}{\underline{Available upon request}}]}

% \begin{multicols}{2}

% 	\textbf{Dr. Jones Owusu Twumasi} \par
% 	Lecturer, Department of Civil Engineering \par
% 	KNUST \par
% 	\href{mailto:jotwumasi@knust.edu.gh}{jotwumasi@knust.edu.gh} \par
% 	{+233 244306788} \vspace*{0.5cm}

% 	\textbf{Dr. Russel Owusu Afrifa} \par
% 	Lecturer, Department of Civil Engineering \par
% 	KNUST \par
% 	\href{mailto:roafrifa.coe@knust.edu.gh}{roafrifa.coe@knust.edu.gh} \par
% 	{+233 551192818} \vspace*{0.5cm}

% 	\columnbreak

% 	\textbf{Ing. Dela Doyen Dakpo} \par
% 	Project Manager / Structural Engineer \par
% 	Quatran Services Limited \par
% 	\href{mailto:quatranlimited@gmail.com}{quatranlimited@gmail.com} \par
% 	{+233 247932961} \vspace*{0.5cm}

% \end{multicols}

\end{document}