\documentclass[letterpaper, 12pt]{article}

\usepackage[margin=1in]{geometry} % page Layout
\usepackage{enumitem} % enumeration labels
\usepackage[hidelinks]{hyperref} % url Links
\usepackage{fontawesome} % icons
\usepackage{xcolor} % colors
\usepackage{fontspec} % font specification
\usepackage{comment} % multiline comment
\usepackage{multicol} % multiple columns
\usepackage{sectsty}
\usepackage{ulem}
\usepackage{fancyhdr}
%\usepackage{ragged2e}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{\faGithub \space \href{https://www.github.com/patrickboateng}{patrickboateng}}
\cfoot{}
\rfoot{\footnotesize{page \thepage}}


\newcommand{\fullwidthuline}[1]{%
	\par\noindent\uline{\hbox to \textwidth{#1\hfil}}\par
}

\sectionfont{\fullwidthuline}

\setlength{\parindent}{0pt}

\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=blue,
}

\setmainfont{SourceSans3}[
Path = ./font/,
Extension = .ttf,
UprightFont = *-Regular,
BoldFont = *-Bold,
ItalicFont = *-Italic,
BoldItalicFont = *-BoldItalic,
]


%%%%% Custom Commands %%%%%%

\newcommand{\cvsection}[1]{
	
	\section*{#1}
	%\rule[20pt]{\linewidth}{0.5pt} % underline
}

\newcommand{\verticalSpace}{4pt}

\begin{document}
	
	%%% Header %%%
	
	\begin{center}
		
	{\huge{\textbf{PATRICK BOATENG}}} \\ [\verticalSpace]
	
	P.O. Box 1694 \, \vrule \, Cantonment-Accra \\ [\verticalSpace]
	
	% Email
	\faEnvelope \space \href{mailto:boatengpatrick456@gmail.com}{\underline{boatengpatrick456@gmail.com}}
	\, \vrule \,
	% Phone
	\faPhone \space (+233) 248253743
	\, \vrule \,
	% Github	
	 \faGithub \space \href{https://www.github.com/patrickboateng}{\underline{patrickboateng}}
	
	\end{center}
	
	% EDUCATION
	
	\cvsection{EDUCATION} 	
	
	\textbf{Bachelor's degree} \hfill \textbf{Sep 2017 - Nov 2021} \\ [\verticalSpace]
	\textbf{Kwame Nkrumah University of Science and Technology}
	
	\begin{itemize}[leftmargin=*]
		
		\item \textbf{Programme}: Bachelor of Science in Civil Engineering
		\item \textbf{Honor}: First Class [3.76/4.0] - \textit{Scholaro GPA Calculator}
		\item \textbf{Thesis}: Predicting the compressive strength of concrete using machine learning techniques.
		\item \textbf{Key Courses}: Introduction to Finite Element Methods \vrule \, Algebra \vrule \, Numerical Analysis \vrule \, Statistics and Probability \vrule \, Differential Equation \vrule \, Soil and Rock mechanics \vrule \, Computer Aided Design (AutoCad) \vrule \, Computer Programming (MATLAB) \vrule \, Construction Management
	
	\end{itemize}
	
	% RESEARCH INTEREST
	
	\cvsection{RESEARCH INTEREST}
	
	\begin{itemize}[leftmargin=*]
		
		\item Finite element analysis of structures
		\item Machine learning and Artificial Intelligence for design optimization
		\item Application of Artificial Intelligence in transportation
		
	\end{itemize}
	
	% WORK EXPERIENCE
	
	\cvsection{WORK EXPERIENCE}
	
	\textbf{Assistant Consulting Engineer} \hfill \textbf{Sep 2022 - Present} \\ [\verticalSpace]
	\textbf{Heureka Consult Limited} \hfill \textbf{Full Time}
	
	\begin{itemize}[leftmargin=*]
		
		\item Performed quality assurance and quality control procedures for construction projects, including overseeing the Cardinal Namdini gold mine's water storage and tailings dams.
		\item Generated project and laboratory reports for the client.
		\item Conducted geotechnical site investigations for road projects, such as the Accra-Ofankor road rehabilitation.		
		\item Analyzed laboratory test results and made engineering judgements.
		\item Conducted an assessment of structural soundness and stability of pre-existing structures.
		\item Developed a Microsoft Excel add-in capable of soil classification, accommodating both the \textbf{Unified Soil Classification System} and the \textbf{American Association of State Highway and Transportation Officials} classification systems.	\href{https://github.com/patrickboateng/geolab/tree/main/geolab-excel-addin}{\underline{\textbf{Project link}}} \\
		
	\end{itemize}
	
	\textbf{IT Consultant} \hfill \textbf{Sep 2021 - Aug 2022} \\ [\verticalSpace]
	\textbf{Kwame Nkrumah University of Science and Technology} \hfill \textbf{National Service Personnel}
	
	\begin{itemize}[leftmargin=*]
		
		\item Provided assistance in the digitization of manual tasks. For example, I developed a simple database using Python and WxPython to keep track of customers whose applications have been processed.
		\item Assisted and consulted in all IT related work. \\
		
	\end{itemize} 
	
	\textbf{Site Engineer} \hfill \textbf{Apr 2020 - Nov 2020} \\ [\verticalSpace]
	\textbf{Quatran Services Limited} \hfill \textbf{Intern}
	
	\begin{itemize}[leftmargin=*]
		
		\item Conducted site supervision and implemented Quality Assurance and Quality Control measures during the construction of the solvent extraction plant for Wilmar Africa.	
		\item Ensured precise execution of structural drawings by interpreting and comprehending the drawings accurately.
		\item Prepared weekly progress reports summarizing all the works completed on-site.
		
	\end{itemize}
	
	% HONORS AND AWARDS
	
	\cvsection{HONORS AND AWARDS}
	
	\begin{itemize}[leftmargin=*]
		
		\item Provost Excellent Students Awards, College of Engineering (KNUST) in year 3
		\item Provost Excellent Students Awards, College of Engineering (KNUST) in year 4
		
	\end{itemize}
	
	% RESEARCH EXPERIENCE
	
	\cvsection{RESEARCH EXPERIENCE}
	
	\textbf{Concrete compressive strength prediction} \hfill \textbf{Mar 2021 - Aug 2021}
	
	\begin{itemize}[leftmargin=*]
		
		\item Employed various machine learning techniques to develop models for predicting the 28th day compressive strength of concrete. \href{https://www.github.com/patrickboateng/compressive-strength-prediction}{\underline{\textbf{Project link}}}
		
	\end{itemize}
	
	% TECHNICAL SKILLS
	
	\cvsection{TECHNICAL SKILLS}
	
	\begin{itemize}[leftmargin=*]
		
		\item \textbf{Programming Languages}: Python \vrule \, C \vrule \, C++ \vrule \, Microsoft Excel VBA
		\item \textbf{Deep Learning Frameworks}: Pytorch
		\item \textbf{Machine Learning}: Scikit-learn \vrule \, XGBoost
		\item \textbf{Data Analysis}: Pandas \vrule \, Numpy
		\item \textbf{Software}: Microsoft Office Excel \vrule \, Latex \vrule \, AutoCad \vrule \, ETABS
		
	\end{itemize}
	
	% PERSONAL PROJECTS
	
	\cvsection{PERSONAL PROJECTS}
	
	\begin{itemize}[leftmargin=*]
		
		\item \textbf{geolab}: An open-source software for geotechnical engineering analysis and modelling. \href{https://www.github.com/patrickboateng/geolab}{\underline{\textbf{Project link}}}
		
		\item \textbf{makepackage}: A Python package for packaging python code. (\textit{Contributor})
		\href{https://github.com/nyggus/makepackage}{\underline{\textbf{Project link}}}
		
	\end{itemize}
	
	% REFERENCES
	
	\cvsection{REFERENCES}
	
	%\textbf{[\href{mailto:boatengpatrick456@gmail.com}{\underline{Available upon request}}]}
	
	\begin{multicols}{2}
		\textbf{Dr. Jones Owusu Twumasi} \\ [4pt]
		Lecturer, Department of Civil Engineering \\ [4pt]
		Kwame Nkrumah University of Science and Technology \\ [4pt]
		\faEnvelopeSquare \space \href{mailto:jotwumasi@knust.edu.gh}{jotwumasi@knust.edu.gh} \\ [4pt]
		\faPhone \space {+233 244306788} \\ [4pt]
		
		\textbf{Dr. Russel Owusu Afrifa} \\ [4pt]
		Snr. Lecturer, Department of Civil Engineering \\ [4pt]
		Kwame Nkrumah University of Science and Technology \\ [4pt]
		\faEnvelopeSquare \space \href{mailto:roafrifa.coe@knust.edu.gh}{roafrifa.coe@knust.edu.gh} \\ [4pt]
		\faPhone \space {+233 551192818} \\
		
		\columnbreak
		
		\textbf{Ing. Dela Doyen Dakpo} \\ [4pt]
		Project Manager / Structural Engineer \\ [4pt]
		Quatran Services Limited \\ [4pt]
		\faEnvelopeSquare \space \href{mailto:quatranlimited@gmail.com}{quatranlimited@gmail.com}\\[4pt]
		\faPhone \space {+233 247932961} \\ [4pt]

	\end{multicols}
	
\end{document}